---
title: "myPackage Vignette"
author: "Ezekiel House"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
abstract: This vignette explains myPackage's how its four functions work and gives example of how to run them.
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width=8, 
  fig.height=6
)
```

```{r setup}
library(myPackage)
```

---

# myncurve

## Description

The `myncurve(mean, sd, a, color)` function takes in user-defined parameters for a **normal distribution**. Using these parameters, it draws the a bell curve about the `mean` with a standard deviation of `sd`. It also shades the lower tail area under the curve up to `x = a`. Then it returns the **probability** of `a`.

## Usage

```{r, include=TRUE}
myncurve(mean = 5, sd = 1, a = 6, color="blue")
```

## Parameters

`mean - Mean of normal distribution function.`

`sd - Standard deviation from the mean.`

`a - Value of P(Y <= a).`

`color - color of the shaded region under curve.`

---

# myddt

## Description

The `myddt(df, cond)` reads in the DDT.csv file and plots the **LENGTH** vs **WEIGHT** of the fish species that the user specifies. 

## Usage

```{r, include=TRUE}
myddt(df = ddt, SPECIES=="CCATFISH", list = FALSE)
```

## Parameters

`df - Data frame to read from (can only be DDT.csv)`

`cond - Species to filter (SPECIES=="")`

`list - "TRUE" or "FALSE" to print the list of values`

---

# mycltu

## Description 

the `mycltu(n, iter, a, b)` function plots a **random uniform distribution** to show how the distribution changes with sample size. 
## Usage

```{r, include=TRUE}
mycltu(n = 10, iter = 1000, a = 0, b = 10)
```

## Parameters

`n - number of different observations`

`iter - number of iterations`

`a - minimum x value`

`b - maximum x value`

---

# myboot2

## Description

The `myboot2()` function applies a **bootstrap method** to a data set for a specified function and returns a graphed confidence interval for the data. The data set `x` contains the values available for random sampling. `fun` is the function applied to these values. `alpha` is the alpha value of the confidence interval.

## Usage

```{r, include=TRUE}
myboot2(iter = 10000, x=(0:10), fun = "mean", alpha= 0.05, cx = 1.5)
```

The above graph is the confidence interval for the mean of the values between 0 and 10, with 95% confidence.

## Parameters

`iter - Number of iterations that the function will make.`

`x - The range of values to sample from`

`fun - The function that will be applied to the data set.`

`alpha - The alpha value for the confidence interval.`

`cx - character expansion factor.`

`... - Further graphical parameters.`


